PM Mungbean meta-analysis

### 2020-02-26 01_Meta-analysis_experiments.Rmd

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
library(dplyr)
library(readr)
library(kableExtra)
library(leaflet)
library(htmltools)
source("R/import_data.R")
```

>>>>

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, leaflet, htmltools)
source("R/import_data.R")
```

### 2020-02-26 02_Preliminary_analysis.Rmd

```{r PA_Libraries, include=FALSE, message=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               lubridate,
               bomrang,
               openxlsx,
               devtools,
               reshape2,
               lme4,
               kableExtra)
source("R/import_data.R")
if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
#source("./getPPD2.R")
theme_set(theme_usq()
)
```

>>>>

```{r PA_Libraries, include=FALSE, message=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               lubridate,
               bomrang,
               openxlsx,
               devtools,
               reshape2,
               lme4,
               kableExtra)
source("R/import_data.R")
if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
#source("./getPPD2.R")
theme_set(theme_usq())
```
